<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{CUSUM Chart with estimated In-Control State}
-->
CUSUM Chart with estimated In-Control State
===========================================
Using Normality Assumptions
---------------------------
The following is a simple application for CUSUM charts, assuming that
all observations are normally distributed.

Based on $n$ past in-control  observations $X_{-n},\dots,X_{-1}$,
the in-control mean is estimated by
$\hat \mu = \frac{1}{n}\sum_{i=-n}^{-1} X_i$
and the in-control variance by
$\hat \sigma^2=\frac{1}{n-1}\sum_{i=-n}^{-1} (X_i-\hat \mu)^2$.
Based on new observations $X_1,X_2,\dots$, the CUSUM chart is then defined by
$$
S_0=0, \quad S_t=\max\left(0,\frac{S_{t-1}+X_t-\hat \mu-\Delta/2}{\hat \sigma}\right).
$$

```{r,echo=FALSE}
set.seed(12381900)
```

The following generates a data set of past observations (replace this with your observed past data).
```{r}
X <-  rnorm(250)
```
```{r,fig=TRUE,fig.width=8,fig.height=3,echo=FALSE}
par(mar=c(4,5,0,0))
plot(-(250:1),X,xlab="t",ylab=expression(X[t]))
```

Next, we initialise and compute the resulting estimate for running the chart - in this case $\hat \mu$ and $\hat \sigma$.
```{r}
library(spcadjust)
chart <- new("SPCCUSUM",model=SPCModelNormal(Delta=1));
xihat <- xiofdata(chart,X)
str(xihat)
```
Calibrating the Chart to a Given Average Run Length (ARL)
---------------------------------------------------

We now compute a threshold that  with roughly 90\%
probability  results in an average run length of at least 100 in control.
This is based on parametric resampling assuming normality
of the observations.

```{r}
cal <- SPCproperty(data=X,nrep=50,
            property="calARL",chart=chart,params=list(target=100),quiet=TRUE)
cal
```
You should
increase the number of bootstrap replications (the argument nrep) for
real applications. Use the parallell option to speed up the bootstrap
by parallel processing. 

Run the chart
---------------------------------------------------

Next, we run  the chart with new observations (that happen to be in-control).
```{r}
newX <- rnorm(100)
S <- runchart(chart, newdata=newX,xi=xihat)
```

```{r,fig=TRUE,fig.width=10,fig.height=4}
par(mfrow=c(1,2),mar=c(4,5,0,0))
plot(newX,xlab="t")
plot(S,ylab=expression(S[t]),xlab="t",type="b",ylim=range(S,cal@res+1,cal@raw))
lines(c(0,100),rep(cal@res,2),col="red")
lines(c(0,100),rep(cal@raw,2),col="blue")
legend("topleft",c("Adjusted Threshold","Unadjusted Threshold"),col=c("red","blue"),lty=1)
```


In the next example, the  chart is run with data that is   out-of-control from time 51 onwards.
```{r}
newX <- rnorm(100,mean=c(rep(0,50),rep(1,50)))
S <- runchart(chart, newdata=newX,xi=xihat)
```

```{r,fig=TRUE,fig.width=10,fig.height=4,echo=FALSE}
par(mfrow=c(1,2),mar=c(4,4,0,0))
plot(newX,xlab="t")
plot(S,ylab=expression(S[t]),xlab="t",type="b",ylim=pmin(range(S,cal@res,cal@raw),15))
lines(c(0,100),rep(cal@res,2),col="red")
lines(c(0,100),rep(cal@raw,2),col="blue")
legend("topleft",c("Adjusted Threshold","Unadjusted Threshold"),col=c("red","blue"),lty=1)
```


