<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{CUSUM Chart based on Logistic Regression Models with Estimated Parameters}
-->
CUSUM Chart with estimated In-Control State
===========================================
Using Nonparametric bootstrap
---------------------------
In this example we consider an application to a CUSUM charts based
on a logistic regression model.

Assume we have $n$ past in-control  data $(Y_{-n},X_{-n}),\ldots,(Y_{-1},X_{-1})$,
where $Y_i$ is a binary response variable and $X_i$ is a corresponding vector
of covariates. 

Suppose that in control
$\mbox{logit}(\mbox{P}(Y_i=1|X_i))=X_i\beta$. A maximum likelihood estimate  $\hat\beta$ of the
parameters is obtained by  the glm function.

For detecting a change to
$\mbox{logit}(\mbox{P}(Y_i=1|X_i))=\Delta+X_i\beta$,
a CUSUM chart based on the cumulative sum of likelihood ratios of the
in-control versus out-of-control model can be defined by (\citep{Steiner2000Msp})
$$S_t=\max(0, S_{t-1}+R_t), \quad S_0=0, $$
where
$$
\exp(R_t)=\frac{\exp(\Delta+X_t\beta)^{Y_t}/(1+\exp(\Delta+X_t\beta))}{\exp(X_t\beta)^{Y_t}/(1+\exp(X_t\beta))}
=\exp(Y_t\Delta)\frac{1+\exp(X_t\beta)}{1+\exp(\Delta+X_t\beta)}.
$$



```{r,echo=FALSE}
set.seed(22381950)
```

The following generates a data set of past observations (replace this
with your observed past data) from the model
$\mbox{logit}(\mbox{P}(Y_i=1|X_i))=-1+x_1+x_2+x_3$
 and distribution of the covariate values as specified below. 
```{r}
n <- 1000
Xlogreg <- data.frame(x1=rbinom(n,1,0.4), x2=runif(n,0,1), x3=rnorm(n))
xbeta <- -1+Xlogreg$x1+Xlogreg$x2+Xlogreg$x3
Xlogreg$y <- rbinom(n,1,exp(xbeta)/(1+exp(xbeta)))
```

Next, we initialise and compute the resulting estimate for running the chart - in this case $\hat \beta$. 
```{r}
library(spcadjust)
chartlogreg <- new("SPCCUSUMlogreg",Delta= 1, formula="y~x1+x2+x3")
xihat <- xiofdata(chartlogreg,Xlogreg)
xihat
```

Calibrating the Chart to a Given Average Run Length (ARL)
---------------------------------------------------

Next find the threshold that with roughly 90\%
probability  results in an average run length of at least 1000 in control. 
You should increase the number of bootstrap replications (the argument nrep) for real applications.

```{r}
cal <- SPCproperty(data=Xlogreg,
            nrep=100,
            property=new("calARLCUSUM",chart=chartlogreg,target=1000))
cal
```

```{r,echo=FALSE}
set.seed(2238195)
```

Run the chart
---------------------------------------------------

Next, we run  the chart with new observations (that are in-control).
```{r}
n <- 100
newXlogreg <- data.frame(x1=rbinom(n,1,0.4), x2=runif(n,0,1), x3=rnorm(n))
newxbeta <- -1+newXlogreg$x1+newXlogreg$x2+newXlogreg$x3
newXlogreg$y <- rbinom(n,1,exp(newxbeta)/(1+exp(newxbeta)))
S <- runchart(chartlogreg, newdata=newXlogreg,xi=xihat)
```


```{r,fig=TRUE,fig.width=10,fig.height=4,echo=FALSE}
par(mfrow=c(1,1),mar=c(4,5,0,0))
plot(S,ylab=expression(S[t]),xlab="t",type="b",ylim=range(S,cal@res+1,cal@raw))
lines(c(0,100),rep(cal@res,2),col="red")
lines(c(0,100),rep(cal@raw,2),col="blue")
legend("topleft",c("Adjusted Threshold","Unadjusted Threshold"),col=c("red","blue"),lty=1)
```

In the next example, the  chart is run with data that is
out-of-control from time 51 and onwards.
```{r}
n <- 100
newXlogreg <- data.frame(x1=rbinom(n,1,0.4), x2=runif(n,0,1), x3=rnorm(n))
outind <- c(rep(0,50),rep(1,50))
newxbeta <- -1+newXlogreg$x1+newXlogreg$x2+newXlogreg$x3+outind
newXlogreg$y <- rbinom(n,1,exp(newxbeta)/(1+exp(newxbeta)))
S <- runchart(chartlogreg, newdata=newXlogreg,xi=xihat)
```

```{r,fig=TRUE,fig.width=10,fig.height=4,echo=FALSE}
par(mfrow=c(1,1),mar=c(4,5,0,0))
plot(S,ylab=expression(S[t]),xlab="t",type="b",ylim=range(S,cal@res+1,cal@raw))
lines(c(0,100),rep(cal@res,2),col="red")
lines(c(0,100),rep(cal@raw,2),col="blue")
legend("topleft",c("Adjusted Threshold","Unadjusted Threshold"),col=c("red","blue"),lty=1)
```





