<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Shewhart Chart with estimated In-Control State}
-->
Shewhart Chart with estimated In-Control State
===========================================
Using Normality Assumptions
---------------------------

Here we consider a simple application to a two-sided Shewhart chart, assuming that
all observations are normally distributed.

Based on $n$ past in-control  observations $X_{-n},\dots,X_{-1}$,
the in-control mean is estimated by
$\hat \mu = \frac{1}{n}\sum_{i=-n}^{-1} X_i$
and the in-control variance by
$\hat \sigma^2=\frac{1}{n-1}\sum_{i=-n}^{-1} (X_i-\hat \mu)^2$.
Based on new observations $X_1,X_2,\dots$ a two-sided Shewhart chart is then defined by
$$
S_t=\frac{X_t-\hat \mu}{\hat \sigma}.
$$
and signals when $|S_t|>c$ for some threshold $c$.

```{r,echo=FALSE}
set.seed(12381900)
```

The following generates a data set of past observations (replace this with your observed past data).
```{r}
X <-  rnorm(250)
```
```{r,fig=TRUE,fig.width=8,fig.height=3,echo=FALSE}
par(mar=c(4,5,0,0))
plot(-(250:1),X,xlab="t",ylab=expression(X[t]))
```

Next, we initialise and compute the resulting estimate for running the chart - in this case $\hat \mu$ and $\hat \sigma$.
```{r}
library(spcadjust)
chartShew <- new("SPCShewNormalCenterScale",twosided=TRUE);
xihat <- xiofdata(chartShew,X)
str(xihat)
```
Calibrating the Chart to a Given Average Run Length (ARL)
---------------------------------------------------

We now compute a threshold that  with roughly 90\%
probability  results in an average run length of at least 769 in control.
This is based on parametric resampling assuming normality
of the observations.  You should
increase the number of bootstrap replications (the argument nrep) for
real applications.

```{r}
cal <- SPCproperty(data=X,nrep=100,
            property=new("calARLShew",chart=chartShew,target=741))
cal
```

Run the chart
---------------------------------------------------

```{r,echo=FALSE}
set.seed(12381951)
```

Next, we run  the chart with new observations (that are in-control).
```{r}
newX <- rnorm(100)
S <- runchart(chartShew, newdata=newX,xi=xihat)
```
```{r,fig=TRUE,fig.width=10,fig.height=4,echo=FALSE}
par(mfrow=c(1,2),mar=c(4,5,0,0))
plot(newX,xlab="t")
plot(S,ylab=expression(S[t]),xlab="t",type="b",ylim=range(S,cal@res+2,cal@raw,-cal@res-1,-cal@raw))
lines(c(0,100),rep(cal@res,2),col="red")
lines(c(0,100),rep(cal@raw,2),col="blue")
lines(c(0,100),-rep(cal@res,2),col="red")
lines(c(0,100),-rep(cal@raw,2),col="blue")
legend("topleft",c("Adjusted Threshold","Unadjusted Threshold"),col=c("red","blue"),lty=1)
```



In the next example, the  chart is run with data that is   out-of-control from time 51 onwards.
```{r}
newX <- rnorm(100,mean=c(rep(0,50),rep(2,50)))
S <- runchart(chartShew, newdata=newX,xi=xihat)
```

```{r,fig=TRUE,fig.width=10,fig.height=4,echo=FALSE}
par(mfrow=c(1,2),mar=c(4,4,0,0))
plot(newX,xlab="t")
plot(S,ylab=expression(S[t]),xlab="t",type="b",ylim=range(S,cal@res+2,cal@raw,-cal@res-1,-cal@raw))
lines(c(0,100),rep(cal@res,2),col="red")
lines(c(0,100),rep(cal@raw,2),col="blue")
lines(c(0,100),rep(-cal@res,2),col="red")
lines(c(0,100),rep(-cal@raw,2),col="blue")
legend("topleft",c("Adjusted Threshold","Unadjusted Threshold"),col=c("red","blue"),lty=1)
```


